`make.modifiers`

### 2020-12-04 inst/gitbook/03_make.modifiers.Rmd
Updated manual (running)

```{r, fig.height = 16, fig.width = 8}
bd.params <- list(speciation = 1, extinction = 1/3)
traits <- make.traits()
stop.rule <- list(max.taxa = 20, max.living = Inf, max.time = Inf)
modifiers <- NULL
events <- NULL
null.error <- NULL

>>>>

```{r, fig.height = 16, fig.width = 8, eval = FALSE}
bd.params <- list(speciation = 1, extinction = 1/3)
traits <- make.traits()
stop.rule <- list(max.taxa = 20, max.living = Inf, max.time = Inf)
modifiers <- NULL
events <- NULL
null.error <- NULL
